New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2024-07-03 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier/FitBit_elsevier/FitBit_elsevier.tex

\usepackage{tabularx}

@@

% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy Institute. E-mail: marek.hlavac at gmail.com
% Date and time: Mo, Jun 24, 2024 - 16:22:09

\\begin{table}[h] 
\\centering 
\\caption{} 
\\label{}
\\begin{tabular}{@{
\\extracolsep{5pt}} ccccc} \\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex] \\textbackslash \textit{Interval} & \\textbackslash \textit{M HR} & \\textbackslash \textit{SD HR} & \\textbackslash \textit{Min} & \\textbackslash \textit{Max} \\\\ \\hline \\\\[-1.8ex] Overall Course of 2h & 90.09/-0.04 & 15.76/0.99 & 51/-4.03 & 164/4.56 \\\\ Pre-teaching interval & 77.95/-1.07 & 11.14/0.57 & 50/-2.68 & 120/2.96 \\\\ Teaching interval & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\\\ Post-teaching interval & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\\\ Interview interval & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\\\ End Interval & 100.8/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\\\ \\hline \\\\[-1.8ex]
\\end{tabular}
\\end{table}

%\input{tab_1.tex}

>>>>

\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{booktabs}

@@

\input{tab_1.tex}
